### 2021-12-22 README.Rmd
UPDATE README
trying to include the targets dependency graph

---
output: github_document
---

@@

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Haul-out behavior and aerial survey detectability of seals in the Bering and Chukchi seas"
```

@@

  - [:file\_folder: R](/R): pipeline functions developed in support or target pipeline
  - [:page\_facing\_up: _targets.R](/_targets.R): target pipeline
  - [:page\_facing\_up: renv.lock](/renv.lock): renv lockfile

>>>>

---
output: github_document
always_allow_html: true
---

@@

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

@@

  - [:file\_folder: R](/R): pipeline functions developed in support of target pipeline
  - [:page\_facing\_up: _targets.R](/_targets.R): target pipeline
  - [:page\_facing\_up: renv.lock](/renv.lock): renv lockfile

The dependency graph for our pipeline is shown below

```{r, echo=FALSE}
library(targets)
targets::tar_glimpse()
```
